Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-11-19 Ben_Manuscripts/structure_paper/response_to_reviewers.tex

    Author reply: We thank the reviewer for their constructive feedback and aim to address all of their concerns.

    \item \begin{quote}
    \textit{As written, it is not clear if the authors are presenting this
	    study as a validation of GAFF and the present equilibration techniques, or
	    whether this study is providing significant new physical insight into these
	    lyotropic liquid crystals. The paper reads a bit more like the former, with a
	    comprehensive discussion of the degree to which five scattering features
	    expected in experiments are predicted in simulations. However, at the same
	    time, the authors make arguments including (1) pores are made from five columns
	    of monomers, (2) that water is present in the "dry" structures, and (3) that a
	    scattering feature comes from tail packing, not tilt: These observations
	    *could* be new physical insight into lyotropic liquid crystal structure, but as
	    presented seem more like hypotheses than conclusions:}

    \end{quote}

    Author reply: We thank the reviewer for offering their interpretation of
    the purpose of our study, as it is important that we properly convey our
    message. The main purpose our work is to give a detailed description of the
    structure of a lyotropic liquid crystal membrane backed by experimental data.
    This work lays a foundation for future transport studies. By matching 2D-WAXS
    data, we have attempted to unveil the most experimentally-consistent structure
    possible. To clarify this purpose, we have modified and added text to the
    paragraph on page \_ of the introduction, in which we state our perceived
    importance of knowing the most experimentally-consistent structure:

    Old text: ``A molecular-level understanding of LLC polymer membrane
    structure, enabled by molecular dynamics (MD) simulations, can provide
    guidelines to reduce the large chemical space available to design monomers for
    creation of separation-specific membranes. Useful molecular-level modeling
    should incorporate a detailed picture of the nanoscopic pore structure, which
    is crucial to understanding the role of monomer structure in solute transport
    and membrane design.

    New text: ``A molecular-level understanding of LLC polymer membrane
    structure, enabled by molecular dynamics (MD) simulations, will enhance our
    comprehension of the role of monomer structure in solute transport and provide
    guidelines to reduce the large chemical space available to design monomers for
    creation of separation-specific membranes. It is important that we model the
    system with a nanoscopic pore structure that is maximally consistent with
    experimental data in order to best approximate the chemical environment experienced
    by solutes in future simulated transport studies."

%This is unlikely to be achieved if one assembled these systems using
%    united atom or coarse grained models due to the large number of potential
%    metastable configurational basins which plague a system like ours which exhibts
%    such slow dynamics.

    We do not intend for this study to be a validation of GAFF for this
    particular system. We believe we would come to similar conclusions using other
    force fields, however validation of this hypothesis is left for a future study.
    We chose GAFF because it is widely used to simulate organic molecules and there
    are no catch-all force fields built for liquid crystal systems. We are interested in
    what information we can gain from a widely-used out-of-the-box force field and in future
    work, we will validate whether GAFF is sufficient for reproducing trends in
    experimental separation properties. To clarify our use of GAFF, we have added
    the following text to Secton~\ref{method:parameterization} of the Methods on
    page ~\pageref{method:parameterization}.

    New text: ``We chose GAFF because it has been parameterized for use with
    organic molecules. Although researchers have optimized force fields, including
    GAFF (cite), for use with liquid crystals, they are often tuned in order to
    reproduce one or more experimental observables. Since liquid crystals exist in
    a wide range of shapes and sizes, including candidate monomers which we may
    study, we chose to stick with a widely used force field. If we
    can reproduce experimental trends using a single 'out-of-the-box' force field,
    then there will be no need to complicate our studies with customized parameter
    sets."

    We have added the following citation:
    %cite1: liquid crystal gaff tuned to get phase transition temperature.

    Since our ultimate goal is to design new monomers for solute-specific
    separations, we will be employing the same techniques used in this work to
    unsynthesized monomers. In most cases, we will not have an experimental dataset
    to use for comparison. Despite all of the structural intricacies which we have
    revealed in this study, one of our main conclusions is that regardless of which
    system we study, the radial distribution of monomer components stays
    consistent. From this, we can hypothesize that we will extract similar
    transport results regardless of which configuration we use to conduct
    transport studies. This is an extremely important finding which may have
    been undersold in the original draft of the manuscript. We have added the
    following concluding paragraph the end of
    Section~\label{section:pore_composition} on
    page~\pageref{addition:pore_composition} in order to drive the point home:

    New text: ``Our observations suggest that the details of transport may be
    relatively independent of the structural differences between different possible
    structures studied here. Despite the structural intricacies that give rise to
    differences between the various metastable basins, all pores are characterized
    by dense, primarily hydrophilic cores with a gradient towards a primarily
    hydrophobic tail region far from the pore center. This implies that we might
    see the same trends in transport properties from any of the systems studied so
    far. Since the ultimate goal of our work is to design new monomers using high
    throughput simulations, achieving that goal becomes tractable without the need
    to optimize every system with an experimental dataset."

    We also modified a paragraph in our conclusion on page \_ to better
    emphasize our point:

    Old text: ``We characterized the environment centered around the membrane
    pores and learned that the pores are generally filled with monomer head groups
    and sodium ions. All dry systems studied showed a similar distribution of
    sodium, head groups and tails while the wet system shows evidence of slight
    swelling, with minor changes in the distributions due to the presence of water
    molecules. We also observed that there is not a hard partition between
    hydrophilic and hydrophobic regions; instead, there is a gradient of chemical
    constituents. This finding raises questions about the nature of size-exclusion
    separations in systems without a well-defined pore size, which potentially
    could enable separations that vary with chemical identity as well as size.

    New text: ``Although exactly reproducing the experimental 2D-WAXS pattern
    required attention to minute structural details, we found that all systems
    showed similar radial distribution functions characterized by a gradual radial
    transition from a dense hydrophlic core to hydrophobic tails. This observation
    enables us to study new systems that have not been experimentally characterized
    with the expectation that any additional structural optimization will not
    greatly influence trends in transport property predictions. The compositional
    gradient itself raises questions about the nature of size-exclusion separations
    in systems without well-defined pore boundaries, which potentially could enable
    separations that vary with chemical identity as well as size."

@@

    \item \begin{quote}
    \textit{1. For the simulations performed here, the authors do make a strong
	    case that 5 columns per core gets the best pore-to-pore spacing (Figure 5).
	    However, insufficient time is accessed to see whether the 4-, 5-, and 6-column
	    initial conditions move towards or away from the expected pore spacing over
	    many-microseconds trajectories. That said, for the quenches performed here,
	    5-columns per core seems more plausible than 4.}
    \end{quote}

    Author reply: We agree with the reviewer that 5 columns-per-core is more
    plausible than 4 and that much longer simulations may provide further
    supporting evidence. However, there is very little motion on the hundreds of
    nanoseconds timescale that we simulated which suggests that we will not gain
    any significant new insight by extending our simulations into the microsecond
    regime. It is not feasible for us to carry out these simulations as it would
    consume our computational resources with little reward.
    %BJC: The following might apply:
    Some confusion may have been generated by agreement of the disordered basin
    6 column-per-pore system with experimental pore spacing. As mentioned in the
    text, the vertical stacking distance between monomers in that system is far too
    large. The columns are `stretched' in the $z$-direction allowing the pores take
    up less space on the $xy$ plane and thus pack closer together.

    \item \begin{quote}    
    \textit{Is this significant physical insight? It is insight, but the
	    authors do not make a compelling case for how 5 columns would change how we
	    think about these crystals, or how it would impact membrane engineering (or
	    more importantly, whether these 5-column structures assemble in the solution
	    phase, or are only locally stable).}
    \end{quote}

    Author reply: We thank the reviewer for pushing us to provide more
    significant physical insight based on the number of monomers per column. The
    number of columns-per-pore influences the pore radius which is important for
    determining the limits of size-exclusion-based separations. It also tells use
    the density of interacting sites within the pore which may play a role in small
    molecule transport. We have added the following text to the main document at
    the end of Section~\ref{M-section:mon_per_pore} on page \_:

    ``The number of columns per pore dictates the density of interaction sites
    within each pore and the pore radius. A higher number of interaction sites will
    surely play a role in transport of molecules that have an affinity for the
    monomer head groups.  The pore radius increases with the number of columns per
    pore (See Figure~\ref{S-fig:pore_radius}.  This radius is likely related to the
    size of the molecules which can be excluded by this type of membrane. We may be
    able to control LLC membrane pore size by selecting monomers that are stable in
    configurations with more columns-per-pore."

@@

    \item \begin{quote}
    \textit{2. The authors make a pretty compelling case that water causes the
    R-double scattering feature by showing its absence when water is added, but
    that the R-double appears and persists for 200ns after the water makes its way
    into the crystal. However, the authors also show that nonuniformly spaced
    monomers can give rise to the R-Double feature, a seeming counterexample to the
    necessity of water.  Is the R-double feature with water because the monomers
    are now irregularly spaced? What happens when the waters are removed and the
    scattering re-performed in Fig 17c(bottom)?}
    \end{quote}

    Author reply: We thank the reviewer for exposing a potentially unclear
    explanation of the origin of R-double. R-double appears in a dry system with
    non-uniformly spaced monomers \textit{only} if $z$-direction position
    restraints are applied to monomer head groups in order to maintain unevenly
    spaced stacking. As soon as the restraints are released, R-double fades and the
    monomer spacing becomes uniform. We modified the text on page \_ in order to more
    clearly convey this message:

@@

    Old text: ``We can also produce R-double if the LLC monomers are not
    uniformly spaced in the $z$-direction, but instead form pairs that stack less
    than 3.7~\AA~apart, with COMs that are spaced 7.4 \AA~ from neighboring pairs
    of monomers (Figure~\ref{fig:staggered_rzplot_norestraints}).  Our force field
    causes our system to tend towards uniformly spaced layers. Simulations of
    unevenly spaced systems are only stable if position restraints are applied to
    heavy atoms of the phenyl rings. Additionally, there is little evidence from QM
    studies of stacked $\pi-\pi$ systems that such uneven stacking could be
    energetically stable.~\cite{tauer_beyond_2005}"

    New text: ``We can also produce R-double if the LLC monomers are not
    uniformly spaced in the $z$-direction, but instead are placed in pairs that
    stack less than 3.7~\AA~apart, with COMs that are spaced 7.4 \AA~ from
    neighboring pairs of monomers (Figure~\ref{fig:staggered_rzplot_norestraints}).
    Simulations of unevenly spaced systems are only stable while position
    restraints are applied to heavy atoms of the phenyl rings. There is little
    evidence from quantum mechanical studies of stacked $\pi-\pi$ systems that such
    uneven stacking could be energetically stable.~\cite{tauer_beyond_2005} As soon
    as we remove position restraints, our system to tends towards uniformly spaced
    monomers."

    R-double is only long-term stable without position restraints if a small
    amount of water is present. We believe that water facilitates the appearance
    of R-double by stabilizing non-uniform spacing through hydrogen bonding, as the
    reviewer suggests. We clarified the text on page \_ in order to make this 
    conclusion clear:

@@

    The reviewer asked us to re-perform the scattering analysis on the same
    system with water molecules removed. We would like to emphasize that we
    attempted to make a similar argument by removing just the head group atoms from
    the trajectory and re-performing the scattering analysis
    (Figure~\ref{M-fig:rdouble_nophenyls}). In the absence of head groups, R-double
    is not present, implying that their structure (which is influenced by the
    presence of water molecules) is responsible for the R-double reflection. For
    completeness, we performed the scattering analysis on the same system with
    water molecules removed, as suggested by the reviewer, and R-double is still
    present. This is the expected result since the structure of water itself does
    not give rise to R-double. We've added the resulting simulated XRD pattern to
    the Supporting Information, Figure~\ref{S-TBD}.

    \item \begin{quote}
    \textit{3. The authors make the case that the R-spots feature comes from the structure of the hexagonal
    tails, not their tilt. The authors should perform the scattering analysis to check if the R-spots are
    present on the tilted-tails they constrain: This quick experiment would nail down their interpretation
    here, or show that the tilted tails are also plausible (but not observed in this model).}
    \end{quote}

    Author reply: We thank the reviewer for their suggestion. We do not deny
    that the tilt of the monomer tails is a plausible explanation for the
    appearance of reflections that resemble R-spots in many liquid crystal systems.
    While the reviewer's suggested experiment is a good idea, its results in this
    case are ambiguous for a couple reasons. First, the tails may still pack
    hexagonally in the tilted configuration which would independently give rise to
    R-spots. Second, it is necessary to impose high force constant (>1000 kJ mol
    nm$^{-2}$) position restraints in order to maintain a tilt angle close to that
    implied by the 2D WAXS data. The resulting high degree of order in the system 
    gives way to reflections which are easily misinterpretted. We have added the
    following text highlighted in red to the text shown on Page \_ in order to
    acknowledge that tail tilt is a valid explanation of R-spot-like reflections 
    and to offer a reason a molecular reason why our monomers in our system do not
    tilt:

@@

    \item \begin{quote}
    \textit{These arguments would be stronger if there weren't so many
	    qualifications about simulation timescales and GAFF, in particular its ability
	    to predict the shortest-scale feature (pi-stacking) for this system. How does
	    everything else change if the force-field were tuned to get that feature
	    correct?}
    \end{quote}

    Author reply: We thank the reviewer for their constructive criticism. Many
    of our findings may be relatively independent of the force fields used, but we
    feel that we should include these qualifications in order to not overstate our
    case. It is common for researchers to run simulations for an insufficient
    length of time and to make bold claims. We acknowledge the shortcomings of our
    techniques in order to inspire other researchers to build on our initial work.

    We agree with the reviewer that we could tune our force field in order to
    exactly reproduce the $\pi-\pi$ stacking distance seen experimentally. Surely
    there will be some structural differences. There are many ways to tune a force
    field in order to achieve this. As stated earlier, we prefer to work with an
    "out-of-the-box" force field since they are widely used and can be applied to
    vast number of systems. The ultimate goal of our work is to create new monomers
    that can achieve specfic separations. If we can gain experimentally-consistent
    insights using our model simulated with GAFF, then we can have increased
    confidence in future predictions generated from systems built with
    unsynthesized monomers.  With that said, we think that it would be interesting
    to repeat our analysis using different and/or optimized force fields in a
    future study in order to comment on the signficance of any differences.

    We have modified the paragraph of our conclusion which describes future
    work (page \_) in order to acknowledge the possibility that a more tuned force
    field could influence our results:

    Old text: ``Future work, based on what has been learned in this study, may
    help further improve the structural agreement between experiment and
    simulation"

    New text: ``  Future work, based on what has been learned in this study,
    may help further improve the structural agreement between experiment and
    simulation and test the sensitivity of our current conclusions to a more
    accurate structure."

@@

    \item \begin{quote}
    \textit{The MD-Structure-Factor repository is not available at the provided
	    github link, nor does it appear to be online anywhere. So, the correctness of
	    that code cannot be checked.}
    \end{quote}

    Author reply: We thank the reviewer for pointing this out and apologize for
    our mistake. The referenced GitHub repository was set to private due to
    miscommunication with our collaborators but it has now been made public. Please
    feel free to read through the code. We have performed checks to ensure that the
    code works properly, especially when simulating monoclinic unit cells. For
    example, we generated test trajectories containing thousands of frames made up
    of configurations of randomly placed point scatterers in a monoclinic unit cell.
    We expect that the simulated diffraction pattern will have a gaussian shape.
    This exact result is shown in the Figure S-\_ of the supporting information.
    With improper treatment of the monoclinic geometry, the gaussian shape is
    skewed into an elliptical shape.

### 2018-11-19 Ben_Manuscripts/structure_paper/Final_Draft.tex
Text written

  % reworking paragraph
  A molecular-level understanding of LLC polymer membrane structure, enabled by
  molecular dynamics (MD) simulations, will enhance our understanding of the role
  of monomer structure in solute transport and provide guidelines to reduce the
  large chemical space available to design monomers for creation of
  separation-specific membranes. It is important that we model the system with
  a nanoscopic pore structure that is maximally consistent with experimental
  data.

  A molecular-level understanding of LLC polymer membrane structure, enabled by
  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. Useful molecular-level modeling should incorporate a detailed
  picture of the nanoscopic pore structure, which is crucial to understanding the
  role of monomer structure in solute transport and membrane design.  Atomistic
  MD simulations can provide the required level of detail (Figure
  \ref{fig:detailed_pore}), assuming the force fields are sufficiently accurate.  With
  such an atomistic model, we can directly observe molecular-level solute
  transport and suggest governing mechanisms. We can also observe how the choice
  of head group interacts with solutes of interest. In addition, we can
  interchange counterions which may influence both the pore size and the strength
  of the Donnan potential.

@@

  We parameterized the interaction potential for the liquid crystal monomer 
  Na-GA3C11 using the Generalized AMBER Force Field (GAFF) 
  \cite{wang_development_2004} with the Antechamber package \cite{wang_automatic_2006} 
  provided with AmberTools16 \cite{case_ambertools16_2016}. We assigned atomic
  charges using the am1bccsym method of \texttt{molcharge} shipped with QUACPAC
  from Openeye Scientific Software. We ran all molecular dynamics simulations 
  using GROMACS 2016 \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.

@@

  \subsection{Atomistic structure of the pore columns}

  We are most interested in the structure and composition of the pores since we
  would like to study transport mechanisms within them. We have shown that the
  tails possess a certain degree of order which is necessary in order to create
  the complex WAXS pattern shown experimentally, but they will not be involved in
  a separation process. We aim to further understand the pore architecture, in
  order to address Question~\ref{point:composition} posed in the Introduction, 
  and observe the differences, if any, between the different plausible equilibrated
  configurations studied so far. In general, the composition of each region, particularly within our
  definition of the pore region, is similar between all systems. This suggests
  that the details of transport may be relatively independent of the structural
  differences between different possible structures studied here.

@@

@@

  We characterized the environment centered around the membrane pores and
  learned that the pores are generally filled with monomer head groups and sodium
  ions. All dry systems studied showed a similar distribution of sodium, head
  groups and tails while the wet system shows evidence of slight swelling, with
  minor changes in the distributions due to the presence of water molecules. We
  also observed that there is not a hard partition between hydrophilic and
  hydrophobic regions; instead, there is a gradient of chemical constituents. This finding raises
  questions about the nature of size-exclusion separations in systems without a
  well-defined pore size, which potentially could enable separations that
  vary with chemical identity as well as size.

%  We learned that we do not need water to create well-defined pore structures.
%  Systems whose pores were filled with varying amounts of water showed a decrease
%  in structuring relative to dry systems. At higher water concentrations, the pores
%  begin to swell, which may be more conducive to transport.

@@

  Future work, based on what has been learned in this study, may help further
  improve the structural agreement between experiment and simulation. 
  Polarizable force fields explicitly including $\pi-\pi$ interactions may be
  able to draw stacked monomers closer together 
  ~\cite{shi_polarizable_2013,kaminski_development_2004,lopes_polarizable_2007}. 
  We can study ensembles of long simulations in order
  to observe more averaged structure and to create more experimentally consistent
  XRD patterns. Extremely long simulations (on the order of \SI{}{\micro s}) may
  be necessary to better quantify the time scales for large scale rearrangements,
  and the precise arrangements themselves.

>>>>

  % reworking paragraph
  A molecular-level understanding of LLC polymer membrane structure, enabled by
  molecular dynamics (MD) simulations, will enhance our comprehension of the role
  of monomer structure in solute transport and provide guidelines to reduce the
  large chemical space available to design monomers for creation of
  separation-specific membranes. It is important that we model the system with a
  nanoscopic pore structure that is maximally consistent with experimental data
  in order to approximate the chemical environment experienced by solutes in 
  future transport studies. Atomistic MD simulations can provide the required
  level of detail (Figure \ref{fig:detailed_pore}), assuming the force fields are
  sufficiently accurate. With such an atomistic model, we can directly observe
  molecular-level solute transport and suggest governing mechanisms. We can also
  observe how the choice of head group interacts with solutes of interest. In
  addition, we can interchange counterions which may influence both the pore size
  and the strength of the Donnan potential.

%  A molecular-level understanding of LLC polymer membrane structure, enabled by
%  molecular dynamics (MD) simulations, can provide guidelines to reduce the large
%  chemical space available to design monomers for creation of separation-specific
%  membranes. Useful molecular-level modeling should incorporate a detailed
%  picture of the nanoscopic pore structure, which is crucial to understanding the
%  role of monomer structure in solute transport and membrane design.  Atomistic
%  MD simulations can provide the required level of detail (Figure
%  \ref{fig:detailed_pore}), assuming the force fields are sufficiently accurate.  With
%  such an atomistic model, we can directly observe molecular-level solute
%  transport and suggest governing mechanisms. We can also observe how the choice
%  of head group interacts with solutes of interest. In addition, we can
%  interchange counterions which may influence both the pore size and the strength
%  of the Donnan potential.

@@

  We parameterized the interaction potential for the liquid crystal monomer
  Na-GA3C11 using the Generalized AMBER Force Field (GAFF)
  \cite{wang_development_2004} with the Antechamber package
  \cite{wang_automatic_2006} provided with AmberTools16
  \cite{case_ambertools16_2016}. We chose GAFF because it has been parameterized
  for use with organic molecules. Although researchers have optimized force
  fields, including GAFF (cite), for use with liquid crystals, they are often
  tuned in order to reproduce one or more experimental observables. Since liquid
  crystals exist in a wide range of shapes and sizes, including candidate
  monomers which we may study, we chose to stick with a widely used force field.
  If we can reproduce experimental trends using a single 'out-of-the-box' force
  field, then there will be no need to complicate our studies with customized
  parameter sets. We assigned atomic charges using the am1bccsym method of
  \texttt{molcharge} shipped with QUACPAC from Openeye Scientific Software. We
  ran all molecular dynamics simulations using GROMACS 2016
  \cite{bekker_gromacs:_1993,berendsen_gromacs:_1995,van_der_spoel_gromacs:_2005,hess_gromacs_2008}.

@@

  \subsection{Atomistic structure of the pore columns}\label{section:pore_composition}

  We are most interested in the structure and composition of the pores since we
  would like to study transport mechanisms within them. We have shown that the
  tails possess a certain degree of order which is necessary in order to create
  the complex WAXS pattern shown experimentally, but they will not be involved in
  a separation process. We aim to further understand the pore architecture, in
  order to address Question~\ref{point:composition} posed in the Introduction,
  and observe the differences, if any, between the different plausible
  equilibrated configurations studied so far. In general, the composition of each
  region, particularly within our definition of the pore region, is similar
  between all systems.

%  This suggests that the details of transport may be
%  relatively independent of the structural differences between different possible
%  structures studied here.

@@

  \label{addition:pore_composition}
  Our observations suggest that the details of transport may be relatively
  independent of the structural differences between different possible structures
  studied here. Despite the structural intricacies that give rive to differences
  between the various metastable basins, all pores are characterized by dense,
  primarily hydrophilic cores with a gradient towards a primarily hydrophobic
  tail region far from the pore center. This implies that we might see the same
  trends in transport properties from any of the systems studied so far. Since
  the ultimate goal of our work is to design new monomers using high throughput
  simulations, achieving that goal becomes tractable without the need to optimize
  every system with an experimental dataset.

@@

% BJC: new text
  Although exactly reproducing the experimental 2D-WAXS pattern required
  attention to minute structural details, we found that all systems showed
  similar radial distribution functions characterized by a gradual radial
  transition from a dense hydrophlic core to hydrophobic tails. This observation
  enables us to study new systems that have not been experimentally characterized
  with the expectation that any additional structural optimization will not
  greatly influence trends in transport property predictions. The compositional
  gradient itself raises questions about the nature of size-exclusion separations
  in systems without well-defined pore boundaries, which potentially could enable
  separations that vary with chemical identity as well as size.

% BJC: old text:
%  We characterized the environment centered around the membrane pores and
%  learned that the pores are generally filled with monomer head groups and sodium
%  ions. All dry systems studied showed a similar distribution of sodium, head
%  groups and tails while the wet system shows evidence of slight swelling, with
%  minor changes in the distributions due to the presence of water molecules. We
%  also observed that there is not a hard partition between hydrophilic and
%  hydrophobic regions; instead, there is a gradient of chemical constituents. This finding raises
%  questions about the nature of size-exclusion separations in systems without a
%  well-defined pore size, which potentially could enable separations that
%  vary with chemical identity as well as size.

@@

  Future work, based on what has been learned in this study, may help further
  improve the structural agreement between experiment and simulation and test
  the sensitivity of our current conclusions to a more accurate structure. 
  Polarizable force fields explicitly including $\pi-\pi$ interactions may be
  able to draw stacked monomers closer together 
  ~\cite{shi_polarizable_2013,kaminski_development_2004,lopes_polarizable_2007}. 
  We can study ensembles of long simulations in order
  to observe more averaged structure and to create more experimentally consistent
  XRD patterns. Extremely long simulations (on the order of \SI{}{\micro s}) may
  be necessary to better quantify the time scales for large scale rearrangements,
  and the precise arrangements themselves.
